Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-03-21 ms.tex
I added an improved time series with aperture corrections applied.

>>>>

The initial time series has huge fluctuations (and even goes negative! due to poor aperture centering at the start).
I used \texttt{photutils.centroid\_2g} to do 2D Gaussian centroiding to choose the aperture positions to start with.
Adding a centroiding routine significantly improves the precision as seen in Figure \ref{fig:secTseries}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{second_t_series.pdf}
\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
This time aperture centroiding was done.
No bias or flat field corrections were applied.}\label{fig:secTseries}
\end{centering}
\end{figure}
